---
title: "Untitled"
output: html_document
---

```{r}
library(tidyverse)
library(broom)
library(Metrics)
```

```{r}
# Read datasets Cleveland_hd.csv into hd_data
hd_data <- read.csv("Cleveland_hd.csv")

# take a look at the first 5 rows of hd_data
head(hd_data,5)
```

2. Converting diagnosis class into outcome variable
```{r}
# Use the mutate() from dplyr to recode our data
hd_data %>% mutate(hd <- ifelse(class>0, 1, 0)) -> hd_data

# recode sex using mutate function and save as hd_data
hd_data %>% mutate(sex <- factor(sex, levels = 0:1, labels = c("Female", "Male"))) -> hd_data
```

3. Identifying important clinical variables
```{r}
# Does sex have an effect? Sex is a binary variable in this dataset, so the appropriate test is chi-squared test
hd_sex <- chisq.test(hd_data$sex, hd_data$hd)

# Does age have an effect? Age is continuous, so we use a t-test
hd_age <- t.test(hd_data$age ~hd_data$hd)

# What about thalach? Thalach is continuous, so we use a t-test
hd_heartrate <- t.test(hd_data$thalach ~hd_data$hd)
```

```{r}
hd_sex
```
We have p-value of less than 0.05 significane level, So we conclude that sex and disease status have a significant association between the two variables

```{r}
hd_age
```
We have p-value of less than 0.05 significane level, So we conclude that average age from who own a disease different from the average age who doesn't have a heart disease


```{r}
hd_heartrate
```
We have p-value of less than 0.05 significane level, So we conclude that average heartrate from who own a disease different from the average heartrate who doesn't have a heart disease

4. Explore the associations graphically (i)
```{r}
# Recode hd to be labelled
hd_data %>% mutate(hd_labelled = ifelse(hd ==0, "No disease", "Disease")) -> hd_data

# Age vs hd
ggplot(data = hd_data, aes(x=hd_labelled, y = age)) + geom_boxplot() + labs(title="Age vs heart disease status Boxplot")
```
From this boxplot we can conclude the median age of patients with heart disease is greater than that of those without heart disease, Seems weird right?

5. Explore the associations graphically (ii)
```{r}
# Sex vs hd
ggplot(data = hd_data, aes(x = hd_labelled, fill = sex)) + geom_bar(position = "fill") + ylab("Sex %") + labs(title = "Sex percentage per Heart Disease Status")
```

6. Explore the associations graphically (iii)
```{r}
# max heart rate vs hd
ggplot(data = hd_data, aes(x=hd_labelled, y = thalach)) + geom_boxplot()
```

7. Putting all three variables in one model
```{r}
# Use glm() from base R and specify the family argument as binomial
model <- glm(data = hd_data, hd~age+sex+thalach, family = "binomial")

# Extract the model summary
summary(model)
```
From the output above, it shows that variable age insignificant to the model, while the remaining variables have a significant effect to the model.

8. Extracting useful information from the model output
```{r}
# Tidy up the coeffictient table
tidy_m <-tidy(model)
tidy_m

# Calculate OR
tidy_m$OR <- exp(tidy_m$estimate)

# Calculate 95% CI and save a slower CI and upper CI
tidy_m$lower_CI <- exp(tidy_m$estimate - 1.96 * tidy_m$std.error)
tidy_m$upper_CI <- exp(tidy_m$estimate + 1.96 * tidy_m$std.error)

# display the updated coefficient table
tidy_m
```

9. Predicted probabilities from our model
```{r}
# Get the predicted probability in our dataset
pred_prob <- predict(model, hd_data, type = "response")

# Create a decision rule using probability 0.5 as cutoff and save the predicted decision into the main data frame
hd_data$pred_hd <- ifelse(pred_prob >= 0.5, 1, 0)

# Create a new dataframe to save a new case information
newdata <- data.frame(age = 50, sex= "Male", thalach = 150)

# predict probability for this new case and print out the predicted value
p_new <- predict(model, newdata, type = "response")
p_new
```

10. Model performance metrics
```{r}
# Calculate auc, accuracy, classification error
auc <- auc(hd_data$hd, hd_data$pred_hd)
accuracy<- accuracy(hd_data$hd, hd_data$pred_hd)
classification_error <- ce(hd_data$hd, hd_data$pred_hd)

# Print out the mertics on to screen
print(paste("AUC=", auc))
print(paste("Accuracy=", accuracy))
print(paste("Classification Error", classification_error))

# Confusion matrix
table(hd_data$hd, hd_data$pred_hd, dnn=c("Actual Status", "Predicted Status"))
```

